The formal verification of the ctm approach to forcing \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2022-08-23 Independence_CH/forcing.tex
Typo spotted during an unauthorized perusal by Miguel :rofl:

\subsection{The fundamental theorems}\label{sec:fundamental-theorems}
At this point, we work inside the locale \isatt{M{\uscore}ctm1} that
assumes $M$ to be
countable and transitive, and satisfies some fragment of
$\ZFC$.
\footnote{%
Namely, Zermelo set theory plus the replacement instances included in
\locale{M{\uscore}ZF1} and \locale{M{\uscore}ZF{\uscore}ground}.
}%
conjunction of the sets This is further extended by assuming a forcing notion
$\lb \PP, {\preceq} ,\1\rb \in M$. The actual implementation reads:

>>>>

\subsection{The fundamental theorems}\label{sec:fundamental-theorems}
At this point, we work inside the locale \isatt{M{\uscore}ctm1} that
assumes $M$ to be
countable and transitive, and satisfies some fragment of
$\ZFC$%
\footnote{%
Namely, Zermelo set theory plus the replacement instances included in
\locale{M{\uscore}ZF1} and \locale{M{\uscore}ZF{\uscore}ground}.
}.
This is further extended by assuming a forcing notion
$\lb \PP, {\preceq} ,\1\rb \in M$. The actual implementation reads:
